Stable Hot Spot Analysis (Draft)

### 2017-06-14 analysis.Rmd
updated colors for G* vs FocalG*

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Zoom level",
     main = "Variable zoom: G* vs Focal G*")

lines(y1, col = "red")
lines(y2, col = "blue")
legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```
```{r zoom-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
zoom_soh <- read_csv("data/zoom_soh.csv")

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Zoom level",
     main = "Variable zoom: G* vs Focal G*")

lines(y1, col = "red")
lines(y2, col = "blue")
legend(1,1, c("G*", "Focal G*"), fill = c("red", "blue"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```

>>>>

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[up]),
     xlab = "Zoom level")

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```

```{r zoom-sohdown, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
zoom_soh <- read_csv("data/zoom_soh.csv")

@@

plot(y1, type = "n", ylim = c(0,1),
     ylab = expression(SoH[down]),
     xlab = "Zoom level")

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
mtext("CI: FMsize and WMsize", line = -1, adj = .98)
```

### 2017-06-14 paper-main.tex
updated colors for G* vs FocalG*

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for zoom}
    \includegraphics[width=\linewidth]{images/SoHZoomUp}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for zoom}
    \includegraphics[width=\linewidth]{images/SoHZoomDown}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH zoom}
  \label{fig:Zoom}
\end{figure}

@@

>>>>

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH zoom}
  \label{fig:Zoom}
\end{figure}

@@

\begin{figure*}[htp]
  \centering

  \begin{tabular}{cccccccc}
    \hline
    \multicolumn{8}{l}{Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \hline
    \multicolumn{8}{l}{G*Multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-demo-zoom-gstar-8}
  \end{tabular}

\end{figure*}
